О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
The main boundary theorem in terms of epsilon

>>>>

We can improve the constant in Theorem~(TODO: ref) if new exact values of $d(2,n)$ are found;
however, the obtained constant is bounded by $3^{1/4}\cdot2^{-3/2}$.
To be precise, we have the following

\begin{theorem}
	For every $\varepsilon > 0$ there exists such a number $k_0$, that for every $k>k_0$ we have the inequality
	\begin{equation}
		d(2,k) \geq k\cdot(3^{1/4}\cdot2^{-3/2} - \varepsilon)
		.
	\end{equation}
\end{theorem}
